Rubin Observatory Scheduling Algorithm and Simulations

### 2022-09-06 ms.tex

Each DDF is scheduled independently. First, we set a desired total number of DDF sequences, a minimum visit depth, and season length.

@@

>>>>

First, we set a desired total number of DDF sequences, a minimum visit depth, and season length. We compute an expected nominal depth for each DDF in 15 minute intervals for the length of the expected survey. We define a desired cumulative number of observations, then schedule DDF sequences to match the desired cumulative distribution under the constraint that the depth be above some value. Each DDF is scheduled independently, and we take no special precautions to prevent collisions between DDF observations.

XXX--I think this is one potential sequence per night, and then we place it at the optimal time in the night?

@@

\begin{figure}
    \epsscale{0.5}
    \plotone{plots/XMM_LSS10years.pdf}\\
    \plotone{plots/XMM_LSS_0.1.pdf}
    \plotone{plots/XMM_LSS_0.2.pdf}
    \caption{Examples of how DDF fields are pre-scheduled. The top plot shows the expected limiting depth for the XMM-LSS field (given nominal seeing conditions) over the course of the survey. The lower plots zoom in on two observing seasons, showing how observations would be scheduled using 90\% and 80\% of the potential season length respectively, with both using the constraint that scheduled observations reach depths deeper than 23.5 mag in $g$.}
    \label{fig:ddf_examples}
    \epsscale{1}
\end{figure}
